NMRlipids Databank: Making data-driven analyses of membrane properties accessible for all

### 2022-12-06 main.tex
Update main.tex

%\subsection{Finding the best models for PC and PE lipid mixtures}
The power of the NMRlipids databank in selecting the best simulation parameters for a specific application is demonstrated for mixtures of PE and PC lipids in Fig.~\ref{fig:POPCPOPEapls} showing area per lipids from available POPC and POPE bilayer simulations in the databank from different force fields at 310\,K. Predictions from different force fields deviate significantly in terms of absolute values and the slope of decrease upon addition of POPE. Because the area per lipid correlates with the average order parameter of $\it{sn}$-1 chain (Fig.~\ref{fig:quality} F), simulations with the best predictions for area per lipids can be selected based on order parameter quality evaluation. Quality evaluation in Fig.~\ref{fig:quality} and direct comparison in Fig.~\ref{fig:POPC_POPE_dataSI} reveal that Slipids ranks 1st for POPC with a clear difference to others, and 2nd for POPE with only marginally lower quality than GROMOS-CKP, therefore being the best selection for studies where packing effects of PE lipids are relevant. 
%The direct comparison with experiments in Fig.~\ref{fig:POPC_POPE_dataSI} in the supplementary information reveals that 
Simulations with CHARMM36 and GROMOS-CKP predict too packed bilayer for POPC (overestimated order in Fig.~\ref{fig:POPC_POPE_dataSI}), while area per lipid for POPC is overstimated in Lipid17. For POPE, 
%order parameters in  Slipids and GROMOS-CKP are close to experiments suggesting that their are per lipids are most reasonable, while
CHARMM36 and Lipid17 predict too packed membranes.

>>>>

%\subsection{Finding the best models for PC and PE lipid mixtures}
The power of the NMRlipids databank in selecting the best simulation parameters for a specific application is demonstrated for mixtures of PE and PC lipids in Fig.~\ref{fig:POPCPOPEapls}, showing areas per lipid from available POPC and POPE bilayer simulations in the databank from different force fields at 310\,K. Predictions from different force fields deviate significantly in terms of absolute values and the slope of decrease upon addition of POPE. Because the area per lipid correlates with the average order parameter of the $\it{sn}$-1 chain (Fig.~\ref{fig:quality} F), simulations with the best predictions for area per lipids can be selected based on order parameter quality evaluation. Quality evaluation in Fig.~\ref{fig:quality} and direct comparison in Fig.~\ref{fig:POPC_POPE_dataSI} reveal that Slipids ranks 1st for POPC with a clear advantage to the others, and 2nd for POPE with only marginally lower quality score than GROMOS-CKP and is therefore the best avilable choice for studies where packing effects of PE lipids are important. 
%The direct comparison with experiments in Fig.~\ref{fig:POPC_POPE_dataSI} in the supplementary information reveals that 
Simulations with CHARMM36 and GROMOS-CKP predict too packed bilayer for POPC (overestimated order in Fig.~\ref{fig:POPC_POPE_dataSI}), while area per lipid for POPC is overstimated in Lipid17. For POPE, 
%order parameters in  Slipids and GROMOS-CKP are close to experiments suggesting that their are per lipids are most reasonable, while
CHARMM36 and Lipid17 predict too packed membranes.
